FAT-Pointer based range addresses

### 2024-02-25 papers/ISMM/FlexPointer/paper.tex
commented out TLB coalesing

\section{Related work}
\subsection{Huge Pages}
This is used to map a very large region of memory to a 
single entry. This small/large region of memory is physically
contiguous. Most implementations of huge pages are size
aligned, For example for the x86 architecture the huge pages 
size are 4KB, 2MB and 1GB pages. 
% \subsection{Tailored page sizes}
\subsection{TLB coalescing}
This leverages the default OS allocator behavior to pack
multiple PTEs into a single TLB entry.

@@

\subsection{FlexPointer}
FlexPointer is based on the RMM<paper reference RMM> paper. FlexPointer
does eagerly allocate pages which are physically contiguous and stores the ID to translate a virtual address 
to physical address on the remaining unused bits on the 64 bit virtual address. 
The paper contribution mentions shifting the TLB lookup to an earlier stage to improve
latency of accessing the TLB entries. FlexPointer immediate queries the 
range TLB rather than the RMM paper which waits for the L1 TLB miss.

>>>>

\section{Related work}
\subsection{Huge Pages}
This is used to map a very large region of memory to a 
single entry. This small/large region of memory is physically
contiguous. Most implementations of huge pages are size
aligned, For example for the x86 architecture the huge pages 
size are 4KB, 2MB and 1GB pages. 
% \subsection{Tailored page sizes}
% TODO later
% \subsection{TLB coalescing}
% This leverages the default OS allocator behavior to pack
% multiple PTEs into a single TLB entry.

@@

\subsection{FlexPointer}
FlexPointer is based on the RMM<paper reference RMM> paper. FlexPointer
does eagerly allocate pages which are physically contiguous and stores the ID to translate a virtual address 
to physical address on the remaining unused bits on the 64 bit virtual address. 
The paper contribution mentions shifting the TLB lookup to an earlier stage to improve
latency of accessing the TLB entries. FlexPointer immediate queries the 
range TLB for translations rather than the RMM paper which waits for the L1 TLB miss.
